Stats Project 2

### 2022-12-12 article.Rmd
Added code to Appendix of article

---
title: "Stats Project 2"
author: Abhay Sharma | AbhaySh4r.github.io
output:
  pdf_document: default
  html_notebook: default
---
```{r include=FALSE}
library(tidyverse)
```

@@

@@

housing = read.csv(file = "train.csv")
a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide")) #pull dataset into R, select paramters for A1.
fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set) #initial naive model, no transform
summary(fit)

@@

fit_transform <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + log(GrLivArea)*Neighborhood, data = a1_set) #transformed model to improve residuals and assumptions
summary(fit_transform)
confint(fit_transform)

@@

```{r}

>>>>

---
title: "Stats Project 2"
author: Abhay Sharma | AbhaySh4r.github.io
output:
  pdf_document: default
  html_notebook: default
---
```{r include=FALSE}
library(tidyverse)
library(plotly)
library(car)
library(caret)
library(olsrr)
library(corrplot)
```

@@

\subsection{Useful Functions}

```{r RMSE function}
ModelRMSE <- function(res){
  retRMSE <- sqrt(mean(res^2))
  return(retRMSE)
}
```

```{r CVPress function}
CVPress <- function(input_model){
  pred_res = resid(input_model)/(1 - lm.influence(input_model)$hat)
  press <- sum(pred_res^2)
  return(press)
}
```

@@

housing = read.csv(file = "train.csv")
test_housing = read.csv(file = "test.csv")
numeric_housing = housing %>% select_if(is.numeric)
#pull dataset into R, select paramters for A1.
a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>%
  filter( Neighborhood == c("NAmes", "Edwards", "BrkSide")) 
#initial naive model, no transform
fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)

summary(fit)

@@

#transformed model to improve residuals and assumptions
fit_transform <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood +
                      log(GrLivArea)*Neighborhood, data = a1_set)

summary(fit_transform)
confint(fit_transform)

@@

```{r echo = TRUE, results = 'hide', fig.show= 'hide'}
fit_numeric = lm(SalePrice ~., data = housing %>% select_if(is.numeric))
transformed_numeric = numeric_housing
transformed_numeric$SalePrice = log(transformed_numeric$SalePrice)
transformed_numeric$LotArea = log(transformed_numeric$LotArea)
t1 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt,
                                             OverallQual, TotRmsAbvGrd, GarageCars,
                                             TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath ))

corrplot(cor(t1)) #visualize correlation to identify which plots are correlated.
#After elimiation, it should be fairly sparsely correlated.

t1fit = lm(SalePrice ~. , data = t1)

#the p-values for these should be fiddled with, 
backt1 = ols_step_backward_p(t1fit, prem = 0.05, details = FALSE)
forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)               
stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)

#---------------------------------Summary Stats of the produced RL sets
summary(backt1$model)
vif(backt1$model)

ModelRMSE(backt1$model$residuals)
CVPress(backt1$model)
#---------------------------------
summary(forwardt1$model)
vif(forwardt1$model)

ModelRMSE(forwardt1$model$residuals)
CVPress(forwardt1$model)
#---------------------------------
summary(stepwiset1$model)
vif(stepwiset1$model)

ModelRMSE(stepwiset1$model$residuals)
CVPress(stepwiset1$model)

# build predictions from set:

#since the original dataset is transformed, the testset needs to be transformed
#as well to account for the change in base.
test_housing$LotArea = log(test_housing$LotArea)

#--------------------------------------------- Backwards Elimination Prediction:

back_pred = predict(backt1$model, test_housing)

#Since the original dataset was transformed, we need to counter-transform to reobtain the
#untransformed data.

real_bp = exp(back_pred)

#combine with ID and export as .csv

real_bp_joined = data.frame(test_housing$Id, real_bp)
colnames(real_bp_joined) = c("Id", "SalePrice")
#if there are any NA, set them to arbitrary 10k price. 
real_bp_joined[is.na(real_bp_joined)]<-10000

write.csv(real_bp_joined, "./Kaggle_backt1_testset.csv", row.names = FALSE)

#-------------------------------------------- Forwards Selection Prediction:

forward_pred = predict(forwardt1$model, test_housing)
real_forward = exp(forward_pred)
real_fp_joined = data.frame(test_housing$Id, real_forward)
real_fp_joined[is.na(real_fp_joined)]<-10000
colnames(real_fp_joined) = c("Id", "SalePrice")
write.csv(real_bp_joined, "./Kaggle_forwardt1_testset.csv", row.names = FALSE)

#-------------------------------------------- Stepwise Selection Prediction:

stepwise_pred = predict(stepwiset1$model, test_housing)
real_step = exp(stepwise_pred)
real_sp_joined = data.frame(test_housing$Id, real_step)
real_sp_joined[is.na(real_sp_joined)]<-10000
colnames(real_sp_joined) = c("Id", "SalePrice")
write.csv(real_sp_joined, "./Kaggle_stepwiset1_testset.csv", row.names = FALSE)
